The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 SI.tex
Complete xr between SI and main for the theoretical alpha part

\section{Theoretical Analysis}
\label{sec:theory}
\subsection{Polarizability-Based Theoretical Model}
\label{ssec:theory-1}
In this section we show in detail the polarizability-based theoretical
framework that leads to the 2D Moss-like relations proposed in the
main text.  Due to its highly anisotropic nature, the wavefunction of
an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
in- and out-of-plane components, similar to the treatment of quantum
wells (QW),\cite{davies_physics_1997} such that
$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
is the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
in the xy-plane. According to the random phase approximation (RPA)
theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $E$ is the eigenenergy of individual bands, and $f$ is the
Fermi-Dirac distribution function. Taking the
limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
at 0 K can be unified by the same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$. Next we will show
that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
give rise to the main text Eqs. \ref{main-eq:2D-Moss-para} and
\ref{main-eq:2D-Moss-perp}.

@@

\subsection{}
\label{sec:theory-2}

>>>>

\section{Theoretical Analysis}
\label{sec:theory}
\subsection{Polarizability-Based Theoretical Model}
\label{ssec:theory-1}
The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ revealed by Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} are not coincidence. Combining recent
theoretical findings of the linear relation between exciton binding
energy $E_{\mathrm{b}}$ and $E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha_{\mathrm{2D}}^{\parallel}$. Moreover, the bandgap-independent relation of
2D $\alpha_{\mathrm{2D}}^{\perp}$ resembles molecular polarizabilities of conjugate
molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
carbon nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent.

In this section we show in detail the polarizability-based theoretical
framework that leads to the 2D Moss-like relations proposed in the
main text.  Due to its highly anisotropic nature, the wavefunction of
an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
in- and out-of-plane components, similar to the treatment of quantum
wells (QW),\cite{davies_physics_1997} such that
$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
is the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
in the xy-plane. According to the random phase approximation (RPA)
theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $E$ is the eigenenergy of individual bands, and $f$ is the
Fermi-Dirac distribution function. Taking the
limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
at 0 K can be unified by the same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$. Next we will show
that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
give rise to the main text Eqs. \ref{main-eq:2D-Moss-para} and
\ref{main-eq:2D-Moss-perp}.

@@

\subsection{Comparing 2D and 3D Moss relations}
\label{sec:theory-2}

### 2018-11-15 paper.tex
Complete xr between SI and main for the theoretical alpha part

\subsection{2D Moss-like  Relations}
\label{sec:first-principles}
Based on the 2D polarizabilities, we then investigate the potential
Moss-like relations for 2D materials. By evaluating the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
treatment\cite{kittel_2005_introduction} (details see Supplementary
Section SXX) \todo{note}, we show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
have simple relation with the electronic  and structural information of a 2D
material, respectively:
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
material, and $\delta$ is its intrinsic
thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
the main conclusions of this work.

To validate such relations, we study several types of 2D materials as
show in Figure \ref{fig-3}a, including transition metal
dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
and thin layer organic-inorganic perovskites (ABX$_{3}$).  For the
TMDCs, we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2
space group) and 1T (P3m1 space group).  The static 2D
polarizabilities are calculated from the static dielectric response of
the selected 2D materials using density functional theory (DFT) with
the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details). Figure \ref{fig-3}b
shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
(bar plots) of all the 2D materials investigated, covering a wide
spectrum range from far infrared to ultraviolet. Note from dimension
analysis, it is more intuitive to express the polarizability as
$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
$E_{\mathrm{g}}$ is observed (see Supplementary Section
\ref{SI-sec:pol-2D-Eg}), which appears to be in good agreement with
our polarizability-based theoretical model (Supplementary Section SXX
\todo{note}). We then examine Eqs. \ref{eq:2D-Moss-para} and
\ref{eq:2D-Moss-perp} using the polarizabilities calculated by first
principle calculations. Figure \ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investiaged (circle dots), with a linear regression
coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
corresponds well with theoretical investigations (details see
Supplementary Section SXX \todo{format Jiang's paper into SI}).
% From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
% $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
% $8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
% yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
% studied.
% We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
% eV) generally lie close to the regression line, while the deviation
% becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
% also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
% 2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}.
We also discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid functionals, compared
with that from the Perdew--Burk--Ernzerhof (PBE) exchange correlations
(details see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
Supplementary Figure \ref{SI-fig:alpha-Eg-diff}), which can be
explained by the fact that the electronic structure, in particular the
bandgap, is generally better predicted at HSE06 level than PBE level
\cite{Heyd_2005}. It should be noted that although even more accurate
estimation of both dielectric properties and bandgap can be achieved
via many-body Green’s function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$. We also show
that the proposed relation behaves equivalently well when using the
experimentally accessible optical bandgap of 2D materials (details see
Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
\ref{SI-fig:opt}).

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c,
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words,
$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is almost identical
to $\delta_{\mathrm{cov}}$, which has its strong physical
meaning. Similar to the molecular polarizability which characterizes
the volume of electron cloud of an isolated molecule
\cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section SXX \todo{note}). In fact, the universal
scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure \ref{fig-3}c indicates
that the quantity $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
(dielectric) characteristic thickness of a 2D material, and can be
used to resolve the long-existing controversy about the experimental
thickness of 2D materials, such as graphene \cite{Shearer_2016}.

\iffalse
The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ revealed by Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} are not coincidence. Combining recent
theoretical findings of the linear relation between exciton binding
energy $E_{\mathrm{b}}$ and $E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha_{\mathrm{2D}}^{\parallel}$. Moreover, the bandgap-independent relation of
2D $\alpha_{\mathrm{2D}}^{\perp}$ resembles molecular polarizabilities of conjugate
molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
carbon nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent.
\fi

>>>>

\subsection{2D Moss-like  Relations}
\label{sec:first-principles}
Based on the 2D polarizabilities, we then investigate the potential
Moss-like relations for 2D materials. By evaluating the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
treatment\cite{kittel_2005_introduction} (details see Supplementary
Section \ref{SI-ssec:theory-1}), we show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
have simple relation with the electronic  and structural information of a 2D
material, respectively:
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
material, and $\delta$ is its intrinsic
thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
the main conclusions of this work.  \todo[inline]{I not sure if we
  need to show the proportional coefficiens
  here. $\alpha_{2D}^{\perp}$ is almost certain to be
  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
  a more complex coefficient.}

To validate such relations, we study several types of 2D materials as
show in Figure \ref{fig-3}a, including transition metal
dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
and thin layer organic-inorganic perovskites (ABX$_{3}$).  For the
TMDCs, we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2
space group) and 1T (P3m1 space group).  The static 2D
polarizabilities are calculated from the static dielectric response of
the selected 2D materials using density functional theory (DFT) with
the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details). Figure \ref{fig-3}b
shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
(bar plots) of all the 2D materials investigated, covering a wide
spectrum range from far infrared to ultraviolet. Note from dimension
analysis, it is more intuitive to express the polarizability as
$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
$E_{\mathrm{g}}$ is observed (see Supplementary Section
\ref{SI-sec:pol-2D-Eg}), which appears to be in good agreement with
our polarizability-based theoretical model (Supplementary Section
\ref{SI-ssec:theory-2}). We then examine Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} using the polarizabilities calculated by
first principle calculations. Figure \ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investiaged (circle dots), with a linear regression
coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
corresponds well with theoretical investigations (details see
Supplementary Section \ref{SI-sssec:theory-1}).  We also discover that
the linearity between
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid functionals, compared
with that from the Perdew--Burk--Ernzerhof (PBE) exchange correlations
(details see Supplementary Section \ref{SI-sec:pol-2D-Eg} and
Supplementary Figure \ref{SI-fig:alpha-Eg-diff}), which can be
explained by the fact that the electronic structure, in particular the
bandgap, is generally better predicted at HSE06 level than PBE level
\cite{Heyd_2005}. It should be noted that although even more accurate
estimation of both dielectric properties and bandgap can be achieved
via many-body Green’s function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$. We also show
that the proposed relation behaves equivalently well when using the
experimentally accessible optical bandgap of 2D materials (details see
Supplementary Section \ref{SI-sec:gpaw-2} and Supplementary Figure
\ref{SI-fig:opt}).

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c,
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words, we
propose
$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0} \approx
\delta_{\mathrm{cov}}$, which has its strong physical meaning. Similar
to the molecular polarizability which characterizes the volume of
electron cloud of an isolated molecule \cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section \ref{SI-sssec:theory-3}). In fact,
the universal scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in
Figure \ref{fig-3}c indicates that the quantity
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
(dielectric) characteristic thickness of a 2D material, and can be
used to resolve the long-existing controversy about the experimental
thickness of 2D materials, such as graphene \cite{Shearer_2016}.
